Paper

### 2020-01-24 Paper.Rmd

## Outline
- General Bayesian computational settings
  - Chains
    - Greta
  - Iterations
  - Warmup
    - STAN/Bugs uses warmup as a part of iterations, Jags/Greta/Nimble have it seperate.
  - Thinning
  - initial value specification
- Each sampler
  - BUGS
    - WINE
    - Debugging
  - Jags
  - Nimble
    - Crashes
  - STAN
    - RDS file
  - Greta
- Common coding techniques for each language
  - Truncated normal
  - Specifiying data and constants
  - Matrix multiplication
  - Initial value specification?
  - sigma / tau
- Benchmarking
  - Run time
  - Memory allocation
  - Computational accuracy
  - Benchmarking files
- Folder design
  - General model type
    - Simple conjugate models
    - Regression models
    - Time Series models
    - Survival models
    - 8 Schools
  - Specific model type
  - Scripts for each method 
  - Benchmarking
- Here package
- Models Used

>>>>

## Outline
- General Bayesian computational settings
  - Chains
    - Greta
  - Iterations
  - Warmup
    - STAN/Bugs uses warmup as a part of iterations, Jags/Greta/Nimble have it seperate.
  - Thinning
  - initial value specification
- Each sampler
  - BUGS
    - WINE
    - Debugging
  - Jags
  - Nimble
    - Crashes
  - STAN
    - RDS file
  - Greta
- Common coding techniques for each language
  - Truncated normal
  - Specifiying data and constants
  - Matrix multiplication
  - Initial value specification?
  - sigma / tau
  - Flat priors
  - Parameter order
    - Binomial Stan has (n,p), rest have (p,n)
- Benchmarking
  - Run time
  - Memory allocation
  - Computational accuracy
  - Benchmarking files
- Folder design
  - General model type
    - Simple conjugate models
    - Regression models
    - Time Series models
    - Survival models
    - 8 Schools
  - Specific model type
  - Scripts for each method 
  - Benchmarking
- Here package
- Models Used
